# Overall outputs

## Timeline {.tabset}

One of the tricky bits about timelines is the format of the date and time of each event. This is different for each event so therefore we have four columns to incorporate this information in the following from for this repository and database. This will also mean that some of the information in other formats will have to be converted into these dimension and any other elements defined in each dataset I am combining to make a overall timeline.

By integrating these stage with some `dataspice` code/approach's allows for me to generate metadata from each sheet of the excel file quickly using R. Here are the steps to do this.

```{r}
#dataspice from github
library(dataspice)

#each project needs to be imported and then saved as csv in raw_data file to document variable names etc correctly into the json dataset.
# raw_data <- 
project2 <- readxl::read_excel("./data/Sem two planning.xlsx", sheet = 4)
project2
#date
data_actions <- readxl::read_excel("./data/Sem two planning.xlsx", sheet = 1)
data_names <- readxl::read_excel("./data/Sem two planning.xlsx", sheet = 3)
#time

#location

```


#### Past Outcomes

```{r}

```


### Action timeline

These sources of data are combined for my general timeline below. These summarised actions are also the flagged tasks from outlook calendar to catch up with this information but this can be automated in the future.

```{r}
# DT::datatable(emailsCalender1)
## handmade data
DT::datatable(data_actions)

# there should be an actions...
data_actions
```

### Future targets

```{r}

```