---
title: "Importing Outlook data"
author: "Anthony Davidson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `.iCal` data

Outlook using iCal files to add appointments and meetings into the outlook calender. Often these files are generated to be added to my calender. These scripts import and re-arrange data into a tidy format. I have defined a baseline database that consists of three key outputs divided by projects:

## Actions


## Timeline

## Project summaries

[coming]

### `.iCal`

For calendars in Outlook the file type is `iCal`. There are only two packages I can find that deal with `.iCal` files in R (`calendar` and `iCal`).

```{r}
#ical data
library(calendar)

f <- system.file("extdata", "england-and-wales.ics", package = "calendar")

ics_df <- ic_read(f)

names(ics_df)

head(ics_df)

vapply(ics_df, class, character(1))

my_cal = ic_dataframe("./data/exportOUTLOOK.ics")
dat1 <-ic_read("./data/exportOUTLOOK.ics")
ic_dataframe(dat1)
my_cal
#> [1] "In Budapest for European R Users Meeting (eRum) conference"
# calculate the duration of the European R users meeting event:
my_cal$`DTEND;VALUE=DATE`[1] - my_cal$`DTSTART;VALUE=DATE`[1]
#> Time difference of 4 days

# ?ic_read()
#export 
list.files(path = "./data/", pattern = "ics")

dat1 <-ic_read("./data/exportOUTLOOK.ics")
dat1 <- ic_list(dat1)
names[dat1]

dat2 <-ic_read("./data/Personal time allocation Calendar.ics")
dat2

dat3 <-ic_read("./data/england-and-wales.ics")
dat3

names(dat1)
names(dat2)
names(dat3)

```

### Outlook API

```{r}
library(RODBC)
library(checkpoint)
# checkpoint("2016-01-01")
```

#### Azure API access

`r #install.packages("AzureGraph")`. Alternatively, you can install the development version from GitHub via `r devtools::install_github("cloudyr/AzureGraph")`.

```{r}
#issues with MCAN microsoft CRAN and RStudio
#july2020

# jose
devtools::install_github("Azure/AzureRMR")

# rappdirs
devtools::install_github("Azure/AzureRMR")

devtools::install_github("Azure/AzureRMR")
devtools::install_github("Azure/AzureGraph")

devtools::install_github("Azure/AzureAuth")
library(AzureRMR)
library(AzureGraph)

# authenticate with AAD
# - on first login, call create_graph_login()
# - on subsequent logins, call get_graph_login()
gr <- create_graph_login()

# account of the logged-in user (if you authenticated via the default method)
me <- gr$get_user()

# alternative: supply an email address or GUID
me2 <- gr$get_user("hongooi@microsoft.com")

# IDs of my groups
head(me$list_group_memberships)
#> [1] "98326d14-365a-4257-b0f1-5c3ce3104f75" "b21e5600-8ac5-407b-8774-396168150210"
#> [3] "be42ef66-5c13-48cb-be5c-21e563e333ed" "dd58be5a-1eac-47bd-ab78-08a452a08ea0"
#> [5] "4c2bfcfe-5012-4136-ab33-f10389f2075c" "a45fbdbe-c365-4478-9366-f6f517027a22"

# a specific group
(grp <- gr$get_group("82d27e38-026b-4e5d-ba1a-a0f5a21a2e85"))
#> <Graph group 'AIlyCATs'>
#>   directory id: 82d27e38-026b-4e5d-ba1a-a0f5a21a2e85
#>   description: ADS AP on Microsoft Teams.
#> - Instant communication.
#> - Share files/links/codes/...
#> - Have fun. :)

```

##### StepbyStep `ical` data 

The two key developers of these packages are:
[Robin Lovelace] 

`Calendar` allows you to read-in `ical files` (which typically have the `.ics` filetype) with `ic_read()`. 

```{r}

```

###### My data

```{r}



s = as.POSIXct("2019-01-12")
e = s + 60^2 * 24 *5
event = ic_event(start = s, end = e , summary = "Research trip")
# event
names(event)
```

```{r}
# key:value pairs in an ical example:
ic_list(ical_example)[[1]]
#>  [1] "DTSTART:20180809T160000Z"                 
#>  [2] "DTEND:20180809T163000Z"                   
#>  [3] "DTSTAMP:20180810T094100Z"                 
#>  [4] "UID:1119ejg4vug5758527atjcrqj3@google.com"
#>  [5] "CREATED:20180807T133712Z"                 
#>  [6] "DESCRIPTION:\\n"                          
#>  [7] "LAST-MODIFIED:20180807T133712Z"           
#>  [8] "LOCATION:"                                
#>  [9] "SEQUENCE:0"                               
#> [10] "STATUS:CONFIRMED"                         
#> [11] "SUMMARY:ical programming mission"         
#> [12] "TRANSP:OPAQUE"
```

```{r}
#import a ical file/or two

list.files(pattern = ".iCal", path = "./data/")
```

`Calendar` also offers a function to create your own simple `ical` object from scratch.

```{r}
# create event

```

###### Creating events

The building blocks of most calendars the event. All events have a start point and an end point (unless they are an all day event) and a summary description. As shown in the example below, they also tend to contain other fields. Fortunately you don’t need to specify all of these when creating events because some will be created manually and some are not necessary. Events can be created as follows (this one creates a 5 day trip):

```{r}
library(calendar)
s = as.POSIXct("2019-01-12")
e = s + 60^2 * 24 *5
event = ic_event(start = s, end = e , summary = "Research trip")
event
#> # A tibble: 1 x 4
#>   UID                         DTSTART             DTEND               SUMMARY   
#>   <chr>                       <dttm>              <dttm>              <chr>     
#> 1 ical-6742dca9-cef7-4377-9c~ 2019-01-12 00:00:00 2019-01-17 00:00:00 Research ~
class(event)
#> [1] "ical"       "tbl_df"     "tbl"        "data.frame"
ic_character(event)
#>  [1] "BEGIN:VCALENDAR"                              
#>  [2] "PRODID:-//ATFutures/ical //EN"                
#>  [3] "VERSION:2.0"                                  
#>  [4] "CALSCALE:GREGORIAN"                           
#>  [5] "METHOD:PUBLISH"                               
#>  [6] "BEGIN:VEVENT"                                 
#>  [7] "UID:ical-6742dca9-cef7-4377-9c05-7bc4913eaacb"
#>  [8] "DTSTART:20190112T000000"                      
#>  [9] "DTEND:20190117T000000"                        
#> [10] "SUMMARY:Research trip"                        
#> [11] "END:VEVENT"                                   
#> [12] "END:VCALENDAR"
```
